### 2019-05-14 manuscript/main.tex
change figure labels

\begin{table}[ht]
\begin{center}
\caption{\textbf{Design principles for climate change mitigation conjoint experiments}}
\label{tab:categories} 
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
\Xhline{2\arrayrulewidth} \\
Who makes the rules? & International organisations; federal government; local government; local community members; non-governmental organisations \\
& \\
Conflict resolution mechanism & United Nations; government bureaucracy; local courts; private arbitration; informal norms \\
& \\
Punishment & Imprisonment; fines; blacklist; none \\
& \\
Punishment for repeated violations & More penalty; same; less penalty \\
& \\
Agreement costs & Rich countries pay more than poor countries; proportional to history of emissions; proportional to current emissions; only rich countries pay \\
& \\
Renegotiation & Never; fifty years; twenty years; five years; one year \\
\Xhline{2\arrayrulewidth} 
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=13cm]{conjoint-cropped.pdf}
	\caption{\textbf{Example of conjoint experiment design}}
	\label{fig:conjoint}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=.9\linewidth,height=11.5cm]{pooled.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement in 10 Latin American countries (pooled data)}}
	\label{fig:pooled}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{countries.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country}}
	\label{fig:countries}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{types.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type}}
	\label{fig:types}
\end{figure}

>>>>

\begin{table}[ht]
\begin{center}
\caption{\textbf{Attributes and values for climate change mitigation conjoint experiments}}
\label{tab:categories} 
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
\Xhline{2\arrayrulewidth} \\
Who makes the rules? & International organisations; federal government; local government; local community members; non-governmental organisations \\
& \\
Conflict resolution mechanism & United Nations; government bureaucracy; local courts; private arbitration; informal norms \\
& \\
Punishment & Imprisonment; fines; blacklist; none \\
& \\
Punishment for repeated violations & More penalty; same; less penalty \\
& \\
Agreement costs & Rich countries pay more than poor countries; proportional to history of emissions; proportional to current emissions; only rich countries pay \\
& \\
Renegotiation & Never; fifty years; twenty years; five years; one year \\
\Xhline{2\arrayrulewidth} 
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=13cm]{conjoint-cropped.pdf}
	\caption{\textbf{Example of conjoint table presented to respondents}}
	\label{fig:conjoint}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=.9\linewidth,height=11.5cm]{pooled.pdf}
	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreements in 10 Latin American countries (pooled data)}}
	\label{fig:pooled}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{countries.pdf}
	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by country}}
	\label{fig:countries}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{types.pdf}
	\caption{\textbf{Effect of institutional attributes on the probability of support for climate change agreement by elite type}}
	\label{fig:types}
\end{figure}
